---
title: "Linear Regression Analysis"
author: "Wanzhi Li"
date: "11/23/2020"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE}
library(RMySQL)
library(aod)
library(ggplot2)
library(ggpubr)
library(pscl)
#library(starpolish)
#library(starpolishr)
library(stargazer)
library(dplyr)
library(lfe)
library(lubridate)
#source("utils/binscatter.R")
#source("utils/utils.R") 
#source("utils/star_panel.R") 
```

## Linear Regression

This document shows the linear regression analysis on relationships between dependent variables and strategy scores. Data are only from 2011.

### Load Data
```{r load data, cache=TRUE}
data = read.csv('prediction_df.csv')
```

```{r}
myvars <- c("X", "seed_founding", "firstrounds_founding","has_ipo",
            "ipo_value","has_tradesale","tradesale_value","tfidf_score",
            "word2vec_score","BERT_score")
model_data = data[myvars]
head(model_data)
```

```{r data_frame}
summary(model_data)
```

### Correlation among scores
```{r correlation, results = "asis"}
correlation <- cor(model_data[,c("tfidf_score","word2vec_score","BERT_score")])
stargazer(correlation, title = "Score Correlation Table", type = 'html', align = TRUE)
```


### Linear model: seed funding

#### baisc linear regression
```{r model1} 
#stargazer(data)
seed_tfidf <- lm(seed_founding ~ tfidf_score, data=model_data)
seed_word2vec <- lm(seed_founding ~ word2vec_score, data=model_data)
seed_BERT <- lm(seed_founding ~ BERT_score, data=model_data)
```


```{r output_table_seed1, results = "asis"}
stargazer(seed_tfidf,seed_word2vec,seed_BERT,title="Linear Regression: seed funding", align=TRUE,type = 'html')
```


```{r viz1, message=FALSE}
p1 <- ggplot(model_data, aes(x = tfidf_score, y = seed_founding)) + 
  geom_point(alpha = 0.5) +
  stat_smooth(method = "lm") + labs(y = "Seed Funding (Million Dollors)")
p2 <- ggplot(model_data, aes(x = word2vec_score, y = seed_founding)) + 
  geom_point(alpha = 0.5) +
  stat_smooth(method = "lm")+ labs(y = "Seed Funding (Million Dollors)")
p3 <- ggplot(model_data, aes(x = BERT_score, y = seed_founding)) + 
  geom_point(alpha = 0.5) +
  stat_smooth(method = "lm")+ labs(y = "Seed Funding (Million Dollors)")

figure <- ggarrange(p1,p2,p3,nrow = 1)
annotate_figure(figure,
               top = text_grob("Linear Regression: seed funding", color = "black", face = "bold", size = 14))
```

#### try to get rid of 0 values in dependent variables
```{r model2}
seed_tfidf <- lm(seed_founding ~ tfidf_score, data=model_data[which(model_data$seed_founding>0),])
seed_word2vec <- lm(seed_founding ~ word2vec_score, data=model_data[which(model_data$seed_founding>0),])
seed_BERT <- lm(seed_founding ~ BERT_score, data=model_data[which(model_data$seed_founding>0),])
```

```{r output_table_seed2, results = "asis"}
stargazer(seed_tfidf,seed_word2vec,seed_BERT,title="Linear Regression: seed funding (remove 0 values)", align=TRUE,type = 'html')
```

```{r viz2, message=FALSE}
p1 <- ggplot(model_data[which(model_data$seed_founding>0),], aes(x = tfidf_score, y = seed_founding)) + 
  geom_point(alpha = 0.5) +
  stat_smooth(method = "lm")
p2 <- ggplot(model_data[which(model_data$seed_founding>0),], aes(x = word2vec_score, y = seed_founding)) + 
  geom_point(alpha = 0.5) +
  stat_smooth(method = "lm")
p3 <- ggplot(model_data[which(model_data$seed_founding>0),], aes(x = BERT_score, y = seed_founding)) + 
  geom_point(alpha = 0.5) +
  stat_smooth(method = "lm")

figure <- ggarrange(p1,p2,p3,nrow = 1)
annotate_figure(figure,
               top = text_grob("Linear Regression: seed funding (remove 0 values)", color = "black", face = "bold", size = 14))
```


### Linear model: first rounds founding
```{r model3} 
#stargazer(data)
first_tfidf <- lm(firstrounds_founding ~ tfidf_score, data=model_data)
first_word2vec <- lm(firstrounds_founding ~ word2vec_score, data=model_data)
first_BERT <- lm(firstrounds_founding ~ BERT_score, data=model_data)
```

```{r output_table3, results = "asis", message=FALSE}
stargazer(first_tfidf,first_word2vec,first_BERT,title="Linear Regression: First rounds founding", align=TRUE,type = 'html')
```

```{r viz3, message=FALSE}
p1 <- ggplot(model_data, aes(x = tfidf_score, y = firstrounds_founding)) + 
  geom_point(alpha = 0.5) +
  stat_smooth(method = "lm")
p2 <- ggplot(model_data, aes(x = word2vec_score, y = firstrounds_founding)) + 
  geom_point(alpha = 0.5) +
  stat_smooth(method = "lm")
p3 <- ggplot(model_data, aes(x = BERT_score, y = firstrounds_founding)) + 
  geom_point(alpha = 0.5) +
  stat_smooth(method = "lm")

figure <- ggarrange(p1,p2,p3,nrow = 1)
annotate_figure(figure,
               top = text_grob("Linear Regression: First rounds founding", color = "black", face = "bold", size = 14))
```


### Linear model: Binary ipo
```{r model4} 
#stargazer(data)
ipo_tfidf <- lm(has_ipo ~ tfidf_score, data=model_data)
ipo_word2vec <- lm(has_ipo ~ word2vec_score, data=model_data)
ipo_BERT <- lm(has_ipo ~ BERT_score, data=model_data)
```


```{r output_table4, results = "asis", message=FALSE}
stargazer(ipo_tfidf,ipo_word2vec,ipo_BERT,title="Linear Regression: Has IPO (binary)", align=TRUE,type = 'html')
```

```{r viz4, message=FALSE}
p1 <- ggplot(model_data, aes(x = tfidf_score, y = has_ipo)) + 
  geom_point(alpha = 0.5) +
  stat_smooth(method = "lm")
p2 <- ggplot(model_data, aes(x = word2vec_score, y = has_ipo)) + 
  geom_point(alpha = 0.5) +
  stat_smooth(method = "lm")
p3 <- ggplot(model_data, aes(x = BERT_score, y = has_ipo)) + 
  geom_point(alpha = 0.5) +
  stat_smooth(method = "lm")

figure <- ggarrange(p1,p2,p3,nrow = 1)
annotate_figure(figure,
               top = text_grob("Linear Regression: Has IPO (Binary)", color = "black", face = "bold", size = 14))
```

### Linear model: Binary Tradesale
```{r model5} 
#stargazer(data)
trade_tfidf <- lm(has_tradesale ~ tfidf_score, data=model_data)
trade_word2vec <- lm(has_tradesale ~ word2vec_score, data=model_data)
trade_BERT <- lm(has_tradesale ~ BERT_score, data=model_data)
```


```{r output_table5, results = "asis", message=FALSE}
stargazer(trade_tfidf,trade_word2vec,trade_BERT,title="Linear Regression: Has Trade Sale (binary)", align=TRUE,type = 'html')
```

```{r viz5, message=FALSE}
p1 <- ggplot(model_data, aes(x = tfidf_score, y = has_tradesale)) + 
  geom_point(alpha = 0.5) +
  stat_smooth(method = "lm")
p2 <- ggplot(model_data, aes(x = word2vec_score, y = has_tradesale)) + 
  geom_point(alpha = 0.5) +
  stat_smooth(method = "lm")
p3 <- ggplot(model_data, aes(x = BERT_score, y = has_tradesale)) + 
  geom_point(alpha = 0.5) +
  stat_smooth(method = "lm")

figure <- ggarrange(p1,p2,p3,nrow = 1)
annotate_figure(figure,
               top = text_grob("Linear Regression: Has Trade Sale (Binary)", color = "black", face = "bold", size = 14))
```

## All Year Data

```{r load data2, cache=TRUE}
All_tfidf = read.csv('/Users/liwangzhi/Documents/GitHub/StartupStrategy/data/TFIDF_with_var.csv')
```

```{r edav}
head(All_tfidf)
```
#### Consider score year and city

```{r linear regression}
gr.reg1 = felm(seed_founding ~ Strat_score|0|0|0, data=All_tfidf)
gr.reg2 = felm(seed_founding ~ Strat_score|score_year|0|score_year, data=All_tfidf)
gr.reg3 = felm(seed_founding ~ Strat_score|score_year+portfoliocompanycity|0|
                 score_year+portfoliocompanycity, data=All_tfidf)
#gr.reg4 = felm(seed_founding ~ Strat_score|0|0|0, data=All_tfidf)
```

```{r output, results = "asis", message=FALSE}
stargazer(gr.reg1,gr.reg2,gr.reg3,
          column.labels=c("OLS","OLS","OLS"),
          add.lines=list(
            c("Score Year F.E.","No","Yes","Yes"),
            c("City F.E.","No","No","Yes")
          ),
          keep=c("Strat_score"),
          title="Linear Regression: seed founding", 
          align=TRUE,type = 'html')
```

#### Consider founding year and state

```{r linear regression2}
gr.reg4 = felm(seed_founding ~ Strat_score|0|0|0, data=All_tfidf)
gr.reg5 = felm(seed_founding ~ Strat_score|incyear|0|incyear, data=All_tfidf)
gr.reg6 = felm(seed_founding ~ Strat_score|incyear+portfoliocompanystatecounty|0|
                 score_year+portfoliocompanystatecounty, data=All_tfidf)
#gr.reg7 = glm(seed_founding ~ Strat_score + as.factor(score_year),data = All_tfidf,family="binomial")
#gr.reg4 = felm(seed_founding ~ Strat_score|0|0|0, data=All_tfidf)
```

```{r output2, results = "asis", message=FALSE}
stargazer(gr.reg4, gr.reg5, gr.reg6,
          column.labels=c("OLS","OLS","OLS"),
          add.lines=list(
            c("Founding Year F.E.","No","Yes","Yes"),
            c("State F.E.","No","No","Yes")
          ),
          keep=c("Strat_score"),
          title="Linear Regression: seed founding", 
          align=TRUE,type = 'html')
```

```{r logistic regression}
gr.reg8 = glm(has_ipo ~ Strat_score, data = All_tfidf)
#gr.reg8 = glm(has_ipo ~ Strat_score + as.factor(score_year), data = All_tfidf)
library(pROC)
resLroc <- roc(gr.reg8)
```

```{r output3, results = "asis", message=FALSE}
stargazer(gr.reg8,
          title="Logistic Regression: Has IPO", align=TRUE,type = 'html')
```

#### next step

- normalize/standardize dependent variable
- add industry into consideration


```{r logistic regression2}
gr.reg7 = glm(has_ipo ~ Strat_score + as.factor(score_year) + as.factor(portfoliocompanycity), data = All_tfidf)
#gr.reg8 = glm(has_ipo ~ Strat_score + as.factor(score_year), data = All_tfidf)
```

```{r output4, results = "asis", message=FALSE}
stargazer(gr.reg7,
          title="Logistic Regression: Has IPO", align=TRUE,type = 'html')
```